On the Functionality of the Multilayer Perceptron

### 2020-11-21 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex
Progress on Back-Propagation section

\paragraph*{}The Rectified Linear Unit (ReLU) activation function acts element-wise on the activations in a given layer. If the activation of a neurons is non-zero or non-negative, the value is untouched, otherwise a $0$ is returned. For an input activation $x$, ReLU is defined by:
\begin{equation}
\label{eqn-ReLU}
\text{ReLU}\big[x\big] = \max\big(0,x\big) = \left\{
\begin{array}{ll}
    x & \text{if\hspace{0.5cm}} x > 0 \\
    0 & \text{otherwise}
\end{array} 
\right.
\end{equation}
ReLU is only defined on a real domain. We provide a visualization of the function in Fig. (\ref{fig-ReLU}).
\begin{figure}[H]
\begin{center}
\includegraphics[scale=0.2]{../Figures/RectifiedLinearUnit}
\end{center}
\caption{Rectifed Linear Unit (ReLU) activation function}
\label{fig-ReLU}
\end{figure}
For our chosen architecture, ReLU is applied to the activations in every single Convolution layer and Dense Layer, with the exception of the output dense layer.

@@

\paragraph*{}By optimizing the parameters $\Theta$ in the network model, we allow for the output of a consistently low cost function to be produced across all samples in the data set.

@@

\paragraph*{}Recall our model of a neural network as a computational graph as in Eq. (\ref{eqn-FunctionGraph}). Each node of the graph is a layer that represents a mathematical function which takes the activation from the previous layer $x^{(l-1)}$ and transforms them into the activations of the current layer, as in Eq. (\ref{eqn-LayerFunction}). Additionally, we recall that each layer itself is made up two steps which produce linear activations such as in Eq. (\ref{eqn-LinearTransform}) and non-linear activations, as in Eq. (\ref{eqn-elementActivation}). Therefore, to understand back propagation, it is necessary to examine the internal functions of each layer. We can use this idea to visualize this chain of operations as in Fig. (\ref{fig-ComputationalGraph})
\begin{figure}[H]
\begin{center}
\textcolor{red}{Graph goes here}
\end{center}
\caption{A visual representation of a computational graph}
\label{fig-ComputationalGraph}
\end{figure}

\paragraph*{}Given this graph chain and it's numerical nature, we cannot compute each element in the gradient vector by conventional symbolic calculus. We must instead use the chain rule for partial derivatives to begin at the final output of the network and successively work our way forward to the entry layer to compute the numerical derivative with respect to each parameter. This process is called \textit{back-propagation} \cite{Geron,Goodfellow,Loy}.

\paragraph*{}We begin by

@@

\subsubsection{The 1-Dimension Vibrating String}

\paragraph*{}We can model a chordophone as having a string of length $L$, with a constant linear mass density, $\mu$, subject to a tension force $F_T$. The string is flexible, and free to vibrate in a single dimension. We describe the state of string over space and time with a function $U(x,t)$. The behavior of the string can be  modeled by D'Alembert's 1-dimensional wave equation \cite{Haberman,Taylor}:
\begin{equation}
\label{eqn-1DWaveEqn}
\frac{\partial^2 U}{\partial t^2} = v^2 \frac{\partial^2 U}{\partial x^2}
\end{equation}
Where $v$ is the wave propagation velocity, given by $\sqrt{\frac{F_T}{\mu}}$. Additionally, the string is fixed in place at both ends, with the nut at $x = 0$ and the bridge at $x = L$, which can be modeled by the boundary conditions:
\begin{equation}
U(0,t) = 0 
	\text{\hspace*{2cm} and \hspace*{2cm}}
U(L,t) = 0 
\end{equation}

@@

\paragraph*{}From each audio file, we produce a spectrogram matrix and a feature vector, as well as a target label for training purpose. From a collection of multiple samples, the spectrograms are concatenated into a single object $X_1$, and the feature vectors are concatenated into an object, $X_2$. Each objects is a multidimensional array called a \textit{design matrix} \cite{Geron,Goodfellow,Loy,Zerizel}. For any machine learning task, a  design matrix is an object that contains real floating-point numbers that store the features in a convenient way for the neural network to digest. For this hybrid neural-network, we use two matrices, $X_1$ and $X_2$, each containing data from $b$ audio file samples. Each has shape given by:
\begin{equation}
\label{eqn-X1Shape}
X_1 \in \mathbb{R}^{(b \times N' \times k \times 1)}
\end{equation}
\begin{equation}
\label{eqn-X2Shape}
X_2 \in \mathbb{R}^{(b \times p)}
\end{equation}
Where $N' \times k \times 1$ gives the shape of the spectrogram matrix $S$ from a single sample, described in sect. (\ref{subsec-spectrogram}). Similarly, $p$ is the number of predictors extracted from each sample, outlined in sec. (\ref{subsec-time}) and sec.(\ref{subsec-frequency}).The first axis, with size $b$ indicates that there are $b$ audio file samples stored in that design matrix.

\paragraph*{}A design matrix is typically accompanied by a \textit{target matrix},$Y$, which indicates the class that the particular sample belongs to. For a classifier with $\kappa$ classes, each sample labeled by a one-hot-encoded vector for shape $1 \times \kappa$ \cite{Tensorflow}. Thus, for the design matrices $X_1$ and $X_2$, we have a corresponding target matrix given by:
\begin{equation}
\label{eqn-YShape}
Y \in \mathbb{R}^{(b \times \kappa)}
\end{equation}

@@

\paragraph*{}The field of neural classification is well studied in the application of image-processing. Many large-scale, and even introductory projects find themselves under the umbrella of image classification \cite{Geron,Goodfellow,Loy,Mierswa}. As a result, model architectures for image processing related tasks are well-explored and have shown experimentally successful behavior. Following this success, it make senses to provide an image-like representation of a sound wave as a feature. We do this in the form of a spectrogram matrix.

\paragraph*{}A spectrogram is a representation of the energy distribution of a sound wave as a function of both frequency and time. In a conventional spectrogram, the passing of time is shown along the $x$-axis, and the frequency spectrum is shown on the $y$-axis. Thus each point in the 2-Dimensional space is an energy at a given time and frequency. Examples spectrograms from the wave form data set are shown in Fig. (\ref{fig-spectrograms}).

\begin{figure}[H]
\begin{center}
\label{fig-spectrograms}
\textcolor{red}{Insert spectrograms here}
\caption{Spectrogram representations of various waveforms}
\end{center}
\end{figure}

@@

\paragraph*{}For this project, we have chosen to use frames of size $N = 4096$ with a $75\%$ or $3072$ sample overlap. Since each audio file contains a different number of samples, we choose the number of frames, $k$ to be less than or equal to $256$. If $k > 256$, the waveform in truncated, if $k \leq 256$ the frames left as is, and missing frames are accounted for later (to improve computation time). The audio has been sampled at $f_s = 44100$ samples/second, so each frame represents a slice of time that is about $0.1$ seconds long.

@@

\paragraph*{}After frame-blocking, we apply a \textit{windowing function} to each frame. A standard \textit{Hann Window} of $N$ samples is generated as a $1 \times N$ row-array, $H$. The $n$-th index in a Hann window with $N$ samples is defined:
\begin{equation}
\label{eqn-Hann}
H[n] = \frac{1}{2}\bigg[ 1 - \cos\Big( \frac{2\pi n}{N-1}\Big)\bigg]
\end{equation}
This window function is applied to each analysis frame by computing the element-wise product of the Hann window array, $H$ and each row of the analysis frames matrix, $A_{i,:}$. The result is another $k \times N$ array, $\widetilde{A}$:
\begin{equation}
\label{eqn-WindowMatrix}
\widetilde{A_i} = A_i \odot H
\end{equation}

\paragraph*{}Window functions are use to account for discontinuities that may arise in the waveform at the edges of each analysis frame. The Fourier Transform assumes that an integer number of signal periods fit within each analysis frame, however this is rarely the case. A transform of this kind of signal can lead to \textit{spectral leakage} where energy appears to "leak" into adjacent frequency bins \textcolor{red}{Citation needed}. This result is a frequency domain that is not an accurate representation of the equivalent time domain. The Hann window uses the raised cosine function to taper the signal off to zero at the end-points, thus eliminate discontinuities at the edges while weighting the samples at the center much more heavily.

\paragraph*{}Finally, we perform a \textit{Discrete Fourier Transform} (DFT) to bring each analysis frame from a time domain into a frequency domain \cite{Olson,Peatross,Virtanen}. The Discrete Fourier Transform is applied by producing an $N \times N$ \textit{transform matrix}, often noted at $\mathbb{W}$. Let $\omega^k = e^{\frac{-2\pi i}{N}k}$, then the DFT matrix for a time-space signal containing $N$ samples
\begin{equation}
\label{eqn-DFTMatrix}
\mathbb{W} = \frac{1}{\sqrt{N}}
\begin{bmatrix}
1 & 1 & 1 & 1 & \hdots & 1 \\
1 & \omega		& \omega^2 & \omega^3 & \hdots & \omega^{N-1} \\
1 & \omega^2	& \omega^4 & \omega^6 & \hdots & \omega^{2(N-1)} \\
1 & \omega^3	& \omega^6 & \omega^9 & \hdots & \omega^{3(N-1)} \\
\vdots & \vdots & \vdots & \vdots & \ddots & \vdots \\
1 & \omega^{N-1} & \omega^{2(N-1)} & \omega^{3(N-1)} & \hdots & \omega^{(N-1)^2}
\end{bmatrix}
\end{equation}
Each column of the matrix is a complex sinusoidal oscillating with an integer number of periods within the $N$-sample length window \cite{Short,Peatross}.The DFT is applied by a taking the matrix - product of $\mathbb{W}$ and $\widetilde{A}^T$. The transpose of $\widetilde{A}$ then makes each analysis frame into a column vector, which gives the appropriate dimension for multiplication.
\begin{equation}
\label{eqn-DFT}
\text{DFT}\big[ \widetilde{A} \big] = \mathbb{W}\widetilde{A}^T
\end{equation}

@@

\paragraph*{}Each spectrogram is now $N' \times k \times 1$ (The last axis represents a single pixel channel, as opposed to $3$ channels for RGB inputs, etc.) and effectively encodes the energy distribution of the waveform as a function of both time and frequency. The spectrogram makes up each sample in the first design matrix $X_1$, Eq.(\ref{eqn-ShapeX1}) used in this model. For this classifier, we have chosen $N' = 558$ and $k = 256$. For training, a batch of $b$ samples are concatenated into a single array object. For a batch of $b$ samples of $N' \times k \times 1$ spectrograms, we shape $X_1$ such that:
\begin{equation}
\label{eqn-X1}
X_1 = \big\{ S^{(0)},S^{(1)},S^{(2)}, ... , S^{(b-1)} \big\} \in \mathbb{R}^{(b \times N' \times k \times 1)}
\end{equation}
Which is consistent with the shape of the $X_1$ matrix outlined in eqn(\ref{eqn-X1Shape}). This matrix is presented to the \textit{Convolution} branch of the neural network for processing.

@@

\paragraph*{}The quantity $TP + FN$ is a measurement of the total number items in that class, independent of selection. Thus, the quantity recall gives the ratio of correct selections to all selectes that were made. More intuitively, we can describe recall as the fraction of relevant items that were selected \cite{Geron}.

@@

\item[•]Dr. Kevin Short and Dr. Maurik Holtrop for various consultation and guidance throughout this project

>>>>

\paragraph*{}The Rectified Linear Unit (ReLU) activation function acts element-wise on the activations in a given layer. If the activation of a neurons is non-zero or non-negative, the value is untouched, otherwise a $0$ is returned. For an input activation $x$, ReLU is defined by:
\begin{equation}
\label{eqn-ReLU}
\text{ReLU}\big[x\big] = \max\big(0,x\big) = \left\{
\begin{array}{ll}
    x & \text{if\hspace{0.5cm}} x > 0 \\
    0 & \text{otherwise}
\end{array} 
\right.
\end{equation}
ReLU is only defined on a real domain. We provide a visualization of the function in Fig. (\ref{fig-ReLU}).
\begin{figure}[H]
\begin{center}
\includegraphics[scale=0.25]{../Figures/RectifiedLinearUnit}
\end{center}
\caption{Rectifed Linear Unit (ReLU) activation function}
\label{fig-ReLU}
\end{figure}
For our chosen architecture, ReLU is applied to the activations in every single Convolution layer and Dense Layer, with the exception of the output dense layer.

@@

\paragraph*{}By optimizing the parameters $\Theta$ in the network model, we allow for the output of a consistently low cost function to be produced across all samples in the data set. When a model produces consistently low cost values across new unseen samples, we consider this to be a \textit{trained} or \textit{fit} model \cite{Goodfellow}.

@@

\paragraph*{}Recall our model of a neural network as a computational graph as in Eq. (\ref{eqn-FunctionGraph}). Each node of the graph is a layer that represents a mathematical function which takes the activation from the previous layer $x^{(l-1)}$ and transforms them into the activations of the current layer, as in Eq. (\ref{eqn-LayerFunction}). Additionally, we recall that each layer itself is made up two steps which produce linear activations such as in Eq. (\ref{eqn-LinearTransform}) and non-linear activations, as in Eq. (\ref{eqn-elementActivation}). Therefore, to understand back propagation, it is helpful to examine the flow of information within each layer. Consider a simplified neural network model visualized in Fig. (\ref{fig-ComputationalGraph})
\begin{figure}[H]
\begin{center}
\includegraphics[scale=0.8]{../Figures/LayerGraph}
\end{center}
\caption{A visual representation of a simplified neural network as a computational graph}
\label{fig-ComputationalGraph}
\end{figure}
Note that we indicate the cost as $J(\Theta)$. This is an allusion to the fact that $J$ depends of both the labels $y$, and the predictions $y^*$. Where $y^*$ is a function of all of the previous layer activation, which are in turn functions of each weight bias element, i.e. the contents of the $\Theta$ object, in Eq. (\ref{eqn-Theta}). This is why we are able to compute the gradient with respect to $\Theta$ as in Eq. (\ref{eqn-CostGradient}).

\paragraph*{}Raw information is presented as $x^{(0)}$ at the top of the figure, and and output is returned as $x^{(L-1)}$ at the bottom. Arrows represent the flow of information. As expressed in Eq. (\ref{eqn-CXELoss}), we compute the cost of a sample, or batch of samples by comparing the difference between $y^*$ (which is $x^{(L-1)}$) and $y$. Given this graph chain and it's numerical nature, we cannot compute each element in the gradient vector through conventional symbolic calculus \cite{Loy}. We must instead use the chain rule for partial derivatives to begin at the final output of the network and successively work our way forward to the entry layer to compute the numerical derivative with respect to each parameter. This process is called \textit{back-propagation} \cite{Geron,Goodfellow}.

\paragraph*{}Suppose we wish to compute the elements of $\frac{\partial J}{\partial W^{(L-1)}}$ and $\frac{\partial J}{\partial b^{(L-1)}}$ for the gradient vector. The flow of information in Fig. (\ref{fig-ComputationalGraph}) indicates that we cannot directly evaluate the derivative because the cost $J$, is a function $x^{(L-1)}$, which is a function of $z^{(L-1)}$, which is a function of elements in $W^{(L-1)}$. Thus, we have:
\begin{equation}
\frac{\partial J}{\partial W^{(L-1)}} = \frac{\partial}{\partial W^{(L-1)}}
\Bigg[ J \bigg\{ x^{(L-1)} \Big[ z^{(L-1)}  \big\{ W^{(L-1)} 
\big\} \Big] \bigg\} \Bigg]
\end{equation}
The evaluation of the derivative of a composite function requires use of the chain rule of multivariate calculus. We represent this symbolically as:
\begin{equation}
\label{eqn-dWL1}
\frac{\partial J}{\partial W^{(L-1)}} = 
\frac{\partial J}{\partial x^{(L-1)}}\frac{\partial x^{(L-1)}}{\partial z^{(L-1)}}\frac{\partial z^{(L-1)}}{\partial W^{(L-1)}}
\end{equation}
Similarly, the partial derivative of the cost with respect to the bias array can be formulated as:
\begin{equation}
\label{eqn-dbL1}
\frac{\partial J}{\partial b^{(L-1)}} = 
\frac{\partial J}{\partial x^{(L-1)}}\frac{\partial x^{(L-1)}}{\partial z^{(L-1)}}\frac{\partial z^{(L-1)}}{\partial b^{(L-1)}}
\end{equation}

\paragraph*{}For the categorical cross entropy cost function, we can evaluate $\partial J / \partial x^{(L-1)}$ over a single sample as:
\begin{equation}
\label{eqn-CXELossDeriv}
\frac{\partial J}{\partial x^{(L-1)}} = \frac{\partial J}{\partial y^*} =
\frac{\partial}{\partial x^{(L-1)}}\big[ -y \log_{10} (y^*) \big] = -\frac{1}{\ln(10)}\sum_{i}\frac{y_{i}}{y^*_i}
\end{equation}
The value $\partial x^{(L-1)} / \partial z^{(L-1)}$ can be found by differentiating Eq. (\ref{eqn-elementActivation}) with respect to the input activations.
\begin{equation}
\frac{\partial x^{(L-1)}}{\partial z^{(L-1)}} = \sigma^{'(l)} \big[ z^{(L-1)} \big]
\end{equation}

\paragraph*{}Suppose we then wish to compute the elements of $\frac{\partial J}{\partial W^{(l)}}$ and $\frac{\partial J}{\partial b^{(l)}}$. Using the same graph from Fig. (\ref{fig-ComputationalGraph}), we can follow the chain of information to derive an expression for the similar to Eq. (\ref{eqn-dWL1}) and Eq. (\ref{eqn-dbL1}) for each layer $(l)$ in the nueral network. In general, we can state that:
\begin{equation}
\label{eqn-dWGeneral}
\end{equation}
And
\begin{equation}
\label{eqn-dbGeneral}
\end{equation}

@@

\subsubsection{The 1-Dimensional Vibrating String}

\paragraph*{}We can model a chordophone as having a string of length $L$, with a constant linear mass density, $\mu$, subject to a tension force $F_T$. The string is flexible, and free to vibrate in a single dimension. We describe the state of string over space and time with a function $U(x,t)$. The behavior of the string can be modeled by D'Alembert's 1-dimensional wave equation \cite{Haberman,Taylor}:
\begin{equation}
\label{eqn-1DWaveEqn}
\frac{\partial^2 U}{\partial t^2} = v^2 \frac{\partial^2 U}{\partial x^2}
\end{equation}
Where $v$ is the wave propagation velocity, given by $\sqrt{\frac{F_T}{\mu}}$. Additionally, the string is fixed in place at both ends, with a nut at $x = 0$ and a bridge at $x = L$, which can be modeled by the boundary conditions \cite{Olson,White,Haberman}:
\begin{equation}
U(0,t) = 0 
	\text{\hspace*{2cm} and \hspace*{2cm}}
U(L,t) = 0 
\end{equation}

@@

\paragraph*{}From each audio file, we produce a spectrogram matrix and a feature vector, as well as a target label for training purpose. From a collection of multiple samples, the spectrograms are concatenated into a single object $X_1$, and the feature vectors are concatenated into an object, $X_2$. Each objects is a multidimensional array called a \textit{design matrix} \cite{Geron,Goodfellow,Loy,Zerizel}. For any machine learning task, a  design matrix is an object that contains real floating-point numbers that store the features in a convenient way for the neural network to digest. For this hybrid neural-network, we use two matrices, $X_1$ and $X_2$, each containing data from $b$ audio file samples. Each has shape given by:
\begin{equation}
\label{eqn-X1Shape}
X_1 \in \mathbb{R}^{(b \times N' \times k)}
\end{equation}
\begin{equation}
\label{eqn-X2Shape}
X_2 \in \mathbb{R}^{(b \times p)}
\end{equation}
Where $N' \times k$ gives the shape of the spectrogram matrix $S$ from a single sample, described in sect. (\ref{subsec-spectrogram}). Similarly, $p$ is the number of predictors extracted from each sample, outlined in sec. (\ref{subsec-time}) and sec.(\ref{subsec-frequency}). The first axis, with size $b$ indicates that there are $b$ audio file samples stored in that design matrix.

\paragraph*{}A design matrix is typically accompanied by a \textit{target matrix} $Y$, which indicates the class that the particular sample belongs to. For a classifier with $\kappa$ classes, each sample labeled by a one-hot-encoded vector for shape $1 \times \kappa$ \cite{Tensorflow,Loy}. Thus, for the design matrices $X_1$ and $X_2$, we have a corresponding target matrix given by:
\begin{equation}
\label{eqn-YShape}
Y \in \mathbb{R}^{(b \times \kappa)}
\end{equation}

@@

\paragraph*{}The application of neural networks to image-processing and recognition has been well studied and developed in the last few decades \cite{Geron,Goodfellow,Loy,Mierswa}. As a result, model architectures for image processing related tasks are well-explored and have shown experimentally successful behavior. Following this success, it make senses to provide an image-like representation of a sound wave as a feature. We do this in the form of a \textit{spectrogram} matrix. A spectrogram is a representation of the energy distribution of a sound wave as a function of both frequency and time. In a conventional spectrogram, the passing of time is shown along the $x$-axis, and the frequency spectrum is shown on the $y$-axis. Thus each point in the 2-Dimensional space is an energy at a given time and frequency. Examples spectrograms from the wave form data set are shown in Fig. (\ref{fig-spectrograms}).
\begin{figure}[H]
\begin{center}
\textcolor{red}{Insert spectrograms here}
\caption{Spectrogram representations of various waveforms}
\label{fig-spectrograms}
\end{center}
\end{figure}

@@

\paragraph*{}For this project, we have chosen to use frames of size $N = 1024$ with a $75\%$ or $768$ sample overlap. Since each audio file contains a different number of samples, we choose the number of frames, $k$ to be less than or equal to $256$. If $k > 256$, the waveform in truncated, if $k \leq 256$ the frames left as is, and missing frames are accounted for later (to improve computation time). The audio has been sampled at $f_s = 44100$ samples/second, so each frame represents a slice of time that is about $0.0232$ seconds long.

@@

\paragraph*{}After frame-blocking, we apply a \textit{windowing function} to each frame. A standard \textit{Hanning Window} of $N$ samples is generated as a $1 \times N$ row-array, $H$. The $n$-th index in a Hanning window with $N$ samples is defined:
\begin{equation}
\label{eqn-Hanning}
H[n] = \frac{1}{2}\bigg[ 1 - \cos\Big( \frac{2\pi n}{N-1}\Big)\bigg]
\end{equation}
This window function is applied to each analysis frame by computing the element-wise product of the Hanning window array, $H$ and each row of the analysis frames matrix, $A_{i,:}$. The result is another $k \times N$ array, $\widetilde{A}$:
\begin{equation}
\label{eqn-WindowMatrix}
\widetilde{A_i} = A_i \odot H
\end{equation}
We show the effect of a Hanning window on a wae 
\begin{figure}[H]

	\begin{subfigure}{1.0\textwidth}
	\centering
	%\includegraphics[width=\textwidth , height=0.2\textheight]{../FiguresFeatures/Auto_Correlation_4}
	\caption{A section of a waveform, $1024$ samples long}
	\end{subfigure}

	\begin{subfigure}{1.0\textwidth}
	\centering
	%\includegraphics[width=\textwidth , height=0.2\textheight]{../FiguresFeatures/Auto_Correlation_4}
	\caption{The Same waveform with a Hanning Window Applied}
	\end{subfigure}

\end{figure}

\paragraph*{}Window functions are use to account for discontinuities that may arise in the waveform at the edges of each analysis frame. The Fourier Transform assumes that an integer number of signal periods fit within each analysis frame, however this is rarely the case. A transform of this kind of signal can lead to \textit{spectral leakage} where energy appears to "leak" into adjacent frequency bins \textcolor{red}{Citation needed}. This result is a frequency domain that is not an accurate representation of the equivalent time domain. The Hanning window uses the raised cosine function to taper the signal off to zero at the end-points, thus eliminate discontinuities at the edges while weighting the samples at the center much more heavily.

\paragraph*{}Before we compute the Fourier Transform to move each analysis frame into frequency-space, we choose to tail-pad each analysis frame with an additional $1024$ samples of all zeros. This means that each frame has gone from being $1024$ samples, to $2048$ samples. Matrix $\widehat{A}$ has a shape of $k \times 2048$. Doubling the size of each analysis frame allows us the synthetically double the resolution in frequency-space, while retaining the resolution in time-space \cite{Virtanen}.

\paragraph*{}With this final change, we perform a \textit{Discrete Fourier Transform} (DFT) to bring each analysis frame from a time domain into a frequency domain \cite{Olson,Peatross,Virtanen}. The Discrete Fourier Transform is applied by producing an $N \times N$ \textit{transform matrix}, often noted at $\mathbb{W}$. Let $\omega^k = e^{\frac{-2\pi i}{N}k}$, then the DFT matrix for a time-space signal containing $N$ samples
\begin{equation}
\label{eqn-DFTMatrix}
\mathbb{W} = \frac{1}{\sqrt{N}}
\begin{bmatrix}
1 & 1 & 1 & 1 & \hdots & 1 \\
1 & \omega		& \omega^2 & \omega^3 & \hdots & \omega^{N-1} \\
1 & \omega^2	& \omega^4 & \omega^6 & \hdots & \omega^{2(N-1)} \\
1 & \omega^3	& \omega^6 & \omega^9 & \hdots & \omega^{3(N-1)} \\
\vdots & \vdots & \vdots & \vdots & \ddots & \vdots \\
1 & \omega^{N-1} & \omega^{2(N-1)} & \omega^{3(N-1)} & \hdots & \omega^{(N-1)^2}
\end{bmatrix}
\end{equation}
Each column of the matrix is a complex sinusoidal oscillating with an integer number of periods within the $N$-sample length window \cite{Short,Peatross}. The DFT is applied by a taking the matrix - product of $\mathbb{W}$ and $\widetilde{A}^T$. The transpose of $\widetilde{A}$ then makes each analysis frame into a column vector, which gives the appropriate dimension for multiplication.
\begin{equation}
\label{eqn-DFT}
\text{DFT}\big[ \widetilde{A} \big] = \mathbb{W}\widetilde{A}^T
\end{equation}

@@

\paragraph*{}Each spectrogram is now $N' \times k$ and effectively encodes the energy distribution of the waveform as a function of both time and frequency. The spectrogram makes up each sample in the first design matrix $X_1$, Eq.(\ref{eqn-ShapeX1}) used in this model. For this classifier, we have chosen $N' = 558$ and $k = 256$. For training, a batch of $b$ samples are concatenated into a single array object. For a batch of $b$ samples of $N' \times k \times 1$ spectrograms, we shape $X_1$ such that:
\begin{equation}
\label{eqn-X1}
X_1 = \big\{ S^{(0)},S^{(1)},S^{(2)}, ... , S^{(b-1)} \big\} \in \mathbb{R}^{(b \times N' \times k)}
\end{equation}
Which is consistent with the shape of the $X_1$ matrix outlined in eqn(\ref{eqn-X1Shape}). This matrix is presented to the \textit{Convolution} branch of the neural network for processing.

@@

\paragraph*{}The quantity $TP + FN$ is a measurement of the total number items in that class, independent of selection. Thus, the quantity recall gives the ratio of correct selections to all selections that were made. More intuitively, we can describe recall as the fraction of relevant items that were selected \cite{Geron}.

@@

\item[•]Dr. Kevin Short and Dr. Maurik Holtrop for various consultation and guidance throughout this project.

\item[•]Dr. Kourosh Zarringhalam and Dr. Marek Petrik for additional consultation on machine learning topics.
